Gravitational field calculation in spherical coordinates using variable densities in depth

### 2019-03-09 manuscript/manuscript.tex
Add missing the before straight line
Add PWL sentences to manuscript

Both the \citet{Lin2018} and the \citet{Fukushima2018} studies limit the radial density
variation to polynomial functions.
While most continuous and smooth functions can be approximated by piecewise linear
functions, the choice of a discretization interval is neither straight forward nor
automatic.
Furthermore, it is well known that the use of high-degree polynomials to approximate a
highly variable function produces unstable results when extrapolating beyond the data
domain.
These shortcomings could make piecewise linear or high-degree polynomial density
functions unwieldy for non-linear gravity inversions \citep[e.g.][]{Uieda2017} if the
density function in depth is highly variable.

@@

\textit{Step 2}:
Evaluate the normalised density function and straight line on a range of $N$ radii
between $r_1$ and $r_2$.
We have opted for $N = 101$ but the specific value of $N$ is not critical to the
algorithm.

>>>>

Both the \citet{Lin2018} and the \citet{Fukushima2018} studies limit the radial density
variation to polynomial functions.
While most continuous and smooth functions can be approximated by piecewise linear
functions, the choice of a discretization interval is neither straight forward nor
automatic for the general case.
Although many piecewise linear approximation algorithms that automatize this process
exist \citep{Ketkov1969, Vandewalle1975, Imamoto2008, Ahmadi2013}, they either require
a fixed number of discretization intervals or are meant to be used only on convex
functions.
They would limit the range of density functions that can be assigned to the tesseroids
or wouldn't guarantee a fully automatic process.
Furthermore, it is well known that the use of high-degree polynomials to approximate a
highly variable function produces unstable results when extrapolating beyond the data
domain.
These shortcomings could make piecewise linear or high-degree polynomial density
functions unwieldy for non-linear gravity inversions \citep[e.g.][]{Uieda2017} if the
density function in depth is highly variable.

@@

\textit{Step 2}:
Evaluate the normalised density function and the straight line on a range of $N$ radii
between $r_1$ and $r_2$.
We have opted for $N = 101$ but the specific value of $N$ is not critical to the
algorithm.
